Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants from 2015 to 2024

### 2024-12-14 paper/paper.qmd
small paper edits for clarity

The variability in the coefficients for predictors l suggests that there may be additional, unobserved variables influencing the likelihood of fatalities that are not captured by the current model. This uncertainty could stem from gaps in the available data or from the limitations in the types of variables collected, such as the lack of detailed road conditions, driver behavior, or vehicle-specific characteristics (e.g., model, age of the vehicle). To reduce this uncertainty, a more comprehensive data collection strategy is needed, focusing on variables that could provide a deeper understanding of accident dynamics, such as weather conditions, road infrastructure quality, or even the socio-economic status of the areas where accidents occur. By expanding the scope and granularity of the data, it would be possible to refine the model, improving the precision of the estimates and providing clearer perspectives into the variables that contribute to fatalities.

>>>>

The variability in the coefficients for predictors suggests that there may be additional, unobserved variables influencing the likelihood of fatalities that are not captured by the current model. This uncertainty could stem from gaps in the available data or from the limitations in the types of variables collected, such as the lack of detailed road conditions, driver behavior, or vehicle-specific characteristics (e.g., model, age of the vehicle). To reduce this uncertainty, a more comprehensive data collection strategy is needed, focusing on variables that could provide a deeper understanding of accident dynamics, such as weather conditions, road infrastructure quality, or even the socio-economic status of the areas where accidents occur. By expanding the scope and granularity of the data, it would be possible to refine the model, improving the precision of the estimates and providing clearer perspectives into the variables that contribute to fatalities.
